CDIPS. I. Light Curves in Open Clusters from TESS Sectors 6 \& 7

### 2019-07-28 paper_I/ms.tex
add a few words

% BEGIN NUMBERS
\newcommand{\numberpcs}{39\ }  % 2019/06/28 unanimous gold
\newcommand{\numberzaripcs}{10\ }  % 2019/06/28 unanimous gold
\newcommand{\numberclusterpcs}{29\ }  % 2019/06/28 unanimous gold
\newcommand{\sVInumberlcs}{67{,}601\ }  % 2019/06/20 not allnan
\newcommand{\sVIInumberlcs}{91{,}736\ }  % 2019/06/20 not allnan
\newcommand{\numberlcs}{159{,}337\ } % 2019/06/20 sum
\newcommand{\numberclusters}{596\ } % 2019/07/01 paper_plot_all_figures.py
\newcommand{\pctoflcswithage}{77} %  2019/07/02 from hist_logt.png

@@

>>>>

% BEGIN NUMBERS
\newcommand{\numberpcs}{39\ }  % 2019/06/28 unanimous gold
\newcommand{\numberzaripcs}{10\ }  % 2019/06/28 unanimous gold
\newcommand{\numberclusterpcs}{29\ }  % 2019/06/28 unanimous gold
\newcommand{\sVInumberlcs}{67{,}612\ }  % 2019/07/27 not allnan
\newcommand{\sVIInumberlcs}{91{,}731\ }  % 2019/07/27 not allnan
\newcommand{\numberlcs}{159{,}343\ } % 2019/06/20 sum
\newcommand{\numberclusters}{596\ } % 2019/07/01 paper_plot_all_figures.py
\newcommand{\pctoflcswithage}{77} %  2019/07/02 from hist_logt.png

@@

Despite our goal being completeness, there may be clusters with
missing members, if those members were not included in any of our
membership catalogs.
A good example is the Orion Nebula (M42; NGC 1976).
While it was observed by TESS in Sector~6, our reduction process resulted in
only 85 light curves being made for its members.
It is known to have far more (CITE OLD PAPER).
This is an issue partially with the membership catalogs, and perhaps
partially with our selection
criteria from them.
For instance,
\cite{cantat-gaudin_gaua_2018} failed to detect it.
\citet{Kharchenko_et_al_2013} lists 42 ``1$\sigma$'' members within
the angular radius of the cluster.
(CITE) DIAS lists 221 objects with prob gt 50, and finite i mags.
A number of the Dias objects maybe were lost in cross-match?! Or else
maybe the stars were dropped or flagged as bad photometry b/c of the
high background?
